NIHAO VII: Predictions for the galactic baryon budget in dwarf to Milky Way mass haloes

### 2016-09-21 ms_nihao_budget.tex
Version revised by Aaron

\voffset=-0.8in

@@

\date{to be submitted to MNRAS}

\pagerange{\pageref{firstpage}--\pageref{lastpage}}\pubyear{2015}

@@

\begin{abstract}
  We use the NIHAO galaxy formation simulations to make predictions
  for the baryonic budget  in present day galaxies ranging from dwarf
  ($\Mhalo\sim10^{10} \Msun$) to Milky Way ($\Mhalo\sim10^{12} \Msun$)
  masses.  The sample is made of 88 independent high resolution
  cosmological zoom-in simulations.  NIHAO galaxies reproduce key
  properties of observed galaxies, such as the stellar mass vs halo
  mass and cold gas vs stellar mass relations. Thus they make
  plausible predictions for the baryon budget.  We present the mass
  fractions of stars, cold gas ($T<10^4$K), cool gas ($10^4 < T <
  10^5$K), warm-hot gas ($10^5 < T < 10^7$K), and hot gas (T$> 10^7$K) 
  , inside the virial radius, $R_{200}$.  Compared to the predicted
  baryon mass, using the dark halo mass and the universal baryon
  fraction, $f_{\rm b}\equiv \Omega_{\rm b}/\Omega_{\rm m}=0.15$, we
  find that all of our haloes are missing baryons. The missing
    mass been relocated past 2 virial radii, and {\bf cool gas dominates
  corona at low mass (M$_{200} \lta 3 \times 10^{11} \Msun$) while the 
  warm-hot gas dominates dominates at high mass (M$_{200} \gta 3 \times 10^{11} \Msun$)}.
   Haloes of mass $\Mhalo\sim 10^{10}\Msun$ are missing
  $\sim 90\%$ of their baryons.  More massive haloes ($\Mhalo\sim
  10^{12}\Msun$) retain a higher fraction of their baryons, with $\sim
  30\%$ missing, consistent with recent observational estimates.
  {\bf Moreover, these more massive haloes reproduce the observed 
  fraction of cold, warm-hot and hot gas, the fraction of cool gas we
  predict is significant lower than the observation from COS-HALOs,
  but agree with the analysis of \citet{Stern16}}.
\end{abstract}

@@

%% missing baryon problem
On cosmological scales, the ratio between the total baryonic and
gravitating mass is measured to be $f_{\rm b}\equiv \Omega_{\rm
  b}/\Omega_{\rm m}\simeq 0.15$ (The Planck Collaboration 2014).
However, the cold baryonic mass density implied by several galaxy baryon
estimates {\bf (mainly about stars and cold gas)} is only 3-8\% of 
the big bang nucleosynthesis expectation
\citep{Persic92, Fukugita98,  Bell03, McGaugh10}.  The majority of the
cosmic baryons are thought to be in the form of hot gas around or
between galaxies \citep{Cen09}. Until recently only a fraction of
these baryons had been detected \citep{Bregman07, Shull12}.  This
discrepancy is referred to as the ``missing baryon problem''.
Several theoretical studies with cosmological simulations
have constrained the phase of
the potential reservoirs of the missing baryons {\bf in intergalactic
medium (IGM), and find a large fraction of the baryons with low density
and high temperature resides between the galaxies}
\citep{Yoshida05, He05, Dave10, Zhu11, Haider16}.

The circum galactic medium (CGM) is {\bf another}  major potential  reservoir
of the missing baryons. \hi{} and metal absorption lines are
expected  to signpost such diffuse baryonic content. \hi{} is mainly
from gas with temperature T $\sim 10^4$ K so that it is able to
detect cold gas in the CGM.  Meanwhile, theoretical work has
predicted that a substantial  portion of the CGM is in the warm or
hot phase with temperature T $> 10^{4.5}$ K.  Gas enters this phase
through photoionization, accretion shocks or shocks caused by
galactic winds \citep{Voort12}. Such dilute halo gas is at T$\sim
10^{4.5-7}$ K, so the detection is dominated by metal lines,
e.g. \ovi{}.  Recent advances in the detection of gas in the CGM
have come  from the COS survey \citep{Tumlinson11, Tumlinson13,
Thom12,  Werk12, Werk13}.  On the scale of Milky Way mass haloes
$\Mhalo \sim 10^{12}\Msun$ a significant amount of warm ($10^4 < T <
10^7$K) gas has been detected \citep{Werk14}, accounting for 33-88\%
of the baryon budget. In the future such observations will be extended
to a wider range of halo masses.  A number of large volume
cosmological simulations \citep{Ford13, Ford15, Suresh15b,
  Oppenheimer16} and zoom-in cosmological simulations
\citep{Stinson12, Hummels13, Shull14} have given 
predictions for the
\hi{} and \ovi{} absorption line. \citet{Gutcke16} compared the
column density profile of \ovi{} and \hi{} in the CGM of galaxies
from the NIHAO \citep{Wang15} cosmological hydrodynamical
simulation suite with observations, studied the covering fraction of
dense \hi{}, looked at the shape of the CGM and its chemical
composition. The conclusion shows {\bf the simulation can reproduce 
the observational covering fraction and column density profile
of cool \hi{} well, and echo observed \ovi{} column density trend.
As commonly in other simulations, however, the column density of \ovi{}
is lower and the extent of optically thick \hi{} is smaller than
observed.}

The physical properties of the CGM has been shown to be able to
test feedback models \citep{Sharma12,Marasco13}.  \citet{Dave09}
predicted galactic halo baryon fractions of galaxies with halo
masses ranging from $10^{11} \Msun$ to $10^{13} \Msun$ using
cosmological hydrodynamical simulations with a well-constrained
model for galactic outflows.  They found that, without the outflow
model, the baryon fraction inside the virial radius is roughly the
cosmic baryonic fraction, but with the outflow model, the baryon
fraction is increasingly suppressed in lower mass haloes.  By
comparing results at $z=3$ and $z=0$, they showed that large
haloes remove their baryons at early times while small haloes lose
baryons more recently due to the wind material taking longer to
return to low-mass galaxies than high-mass galaxies.
{\bf \citet{Muratov15} showed similar results that the gas and
baryon fractions are lower at lower redshift, after powerful
outflows at intermediate redshift z $\approx 0.5-2$ remove a large
amount of gas from the halo. \citet{Voort16} found baryon fraction
and gas fraction are reduced compared to the cosmic mean baryon
fraction, and low mass haloes reduce larger since feedback can
easily expel gas from it, which is consistent with existing 
observation.}
%  
\citet{Sokolowska16} studied the halo gas of three Milky way-sized
galaxies using cosmological zoom-in simulations. They found that
most of missing baryons actually resides in warm-hot and hot gas
which contribute to 80\% of the total gas reservoir.  The recovered
baryon fraction within 3 virial radii is 90\%.  The warm-hot medium
is sensitive to the feedback model so that a reliable spatial
mapping of the warm-hot medium will provide  a stringent test for
feedback models.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

In this study we use simulations from the NIHAO (Numerical
Investigation of a Hundred Astrophysical Objects) project \citep{Wang15}.  
The initial conditions are created to keep the same numerical
resolution across the whole mass range with typically a million dark
matter particles inside the virial radius of the target halo at 
redshift $z=0$.  The halos to be re-simulated at higher resolution
with baryons have been extracted from 3 different pure N-body
simulations with a box size of 60, 20 and 15 $h^{-1}$ Mpc
respectively.  We adopted the  latest compilation of cosmological
parameters from the Planck  satellite \citep{Planck14}. 
More information on the collisionless parent simulations,
{\bf the force softenings and particle masses for the highest 
refinement level for each simulation} and
sample  selection can be found in \citet{Dutton14} and \citet{Wang15}

@@

khe star formation and feedback modeling follows what
was used in the MaGICC simulations \citep{Stinson13}.  
{\bf The gas converts into stars according to the Kennicutt-Schmidt Law
when it satisfies a temperature and density threshold. Stars feed both
metals and energy back into the ISM gas surrounding the region where
they formed. SN feedback is implemented using the blastwave formalism
described in \citet{Stinson06}. Pre-SN feedback is an effort to consider
radiation energy from massive stars which is am important complementary
to physcial model for stellar feedback. Heating is introduced immediately
after massive stars form based on how much star light is radiated. 
Our simulations use thermal feedback to provide pressure support and 
increase gas temperature above the star formation threshold to
decrease star formation.}
There are two
small changes in NIHAO simulations: The change in  number of neighbors
and the new combination of softening length and  particle mass increases
the threshold for star formation from  9.3 to 10.3
cm$^{-3}$, the increase of pre-SN feedback efficiency $\epsilon_{\rm
  ESF}$, from 0.1 to 0.13.  The more detail on star formation and
feedback modeling can be found in \citet{Wang15}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% SECTION 3 RESULTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\section{Results}
%\label{sec:results}

%% FIGURE 1
\begin{figure}
\centerline{
%  \psfig{figure=barbudget_linear_v3.eps,width=0.5\textwidth}}
%\centerline{
%  \psfig{figure=barbudget_v3.eps,width=0.5\textwidth}
  \psfig{figure=barbudget_linearlog.eps,width=0.48\textwidth}
}
\caption{Fractional baryon content of our NIHAO simulations  as a
  function of halo mass. The green points show the ratio between the
  baryonic mass (stars + gas) inside the virial radius and the total
  baryonic mass associated with the dark matter halo. The blue points
  show the corresponding fraction for the stars. The solid green line
  and shaded region shows a double power-law fit, together with the
  1$\sigma$ scatter. For the stellar mass fraction we show several
  relations from halo abundance matching.    The linear (upper panel)
  and logarithmic (lower panel) scales emphasize the large amount of
  ``missing'' baryons, and the power-law nature of the relations,
  respectively.}
\label{fig:budget}
\end{figure}

%% FIGURE 2
\begin{figure}
\centerline{
  \psfig{figure=m500c_frac.eps,width=0.48\textwidth}
}
\caption{{\bf Baryon fraction within R$_{500}$ comparing with \citet{Voort16}.
   The blue points are from NIHAO simulations and the red pentagons are from
   FIRE simulations.}}
\label{fig:fire_com}
\end{figure}

%% FIGURE 3
\begin{figure}
\centerline{
  \psfig{figure=budget_res.eps,width=0.48\textwidth}
}
\caption{{\bf Linear fractional baryon content of our NIHAO simulations  as a
  function of halo mass color coded by number of all particles per halo.}}
\label{fig:budget_res}
\end{figure}

@@

The trends of each component fraction are similar, in that  the
fractions are relatively low in low mass haloes, and increase as the
halo mass increases.  The main difference between the different
components is the slope, with the baryonic mass fraction having a
shallower slope than the stellar mass fraction.  This is because in
low mass haloes ($\Mhalo\sim 10^{10}\Msun$) most of the baryons are in
the form of gas, while in the highest mass haloes we study
($\Mhalo\sim 10^{12}\Msun$) {\bf a substantial amounts of gas
forms stars}.

{\bf \citet{Christensen16} run twenty galaxy simulations spanning the mass range
from $10^{9.5} - 10^{12} \Msun$ using zoom-in cosmological hydrodynamic 
simulation code and didn't only reproduce the stellar mass - halo mass
relation but also showed a similar baryon fraction relation, e.g. in 
L$^*$ galaxies, the fraction is reduced by 20\% while in galaxies with
halo mass $< 10^{10} \Msun$ there can be as large as an 80\% mass reduction.
This suggests that the potential well of the halo regulates the baryon
fraction.
To compare with baryon fraction in \citet{Voort16}, we derive
the M$_{500}$ and R$_{500}$ to recalculate the ratio between 
baryon fraction to the universal fraction of baryons. The baryon
fraction have good agreement with each other in the whole mass range
where NIHAO simulations explored. For the massive haloes with 
M$_{500} > 10^{12} \Msun$, there are two galaxies from NIHAO have
reduced baryon fraction and four more massive galaxies from FIRE
have larger reduced baryon fraction which may hint that the baryon
fraction will decrease as the halo mass increases in large mass range.}

Since most of the haloes we study are above the mass where the cosmic UV
background prevents gas from cooling, the missing baryons have most
likely been ejected from the central galaxies in supernova/stellar
feedback driven winds.  Although the lower mass galaxies have
converted a smaller fraction of their available baryons into stars,
and hence there is proportionally less energy available to drive an
outflow, they have expelled a larger fraction of their baryons,
consistent with expectations from energy driven gas outflows
\citep[e.g.,][]{Dutton12}.

The behavior of the baryonic mass fraction, $f_{\rm bar}$, as a 
function of the halo mass is captured using a double power law formula:
\begin{equation}
\frac{f}{f_0} = \left( 
                        \frac{M_{200}}{\mathcal{M}_0} 
                        \right)^\alpha 
                        \left\{ 0.5 \left[ 1+\left( 
                        \frac{M_{200}}{\mathcal{M}_0} 
                        \right)^\gamma \right] 
                        \right\}^{\frac{\beta-\alpha}{\gamma}}.
\end{equation}
In this formula, the lower and higher mass ends have logarithmic slope
$\alpha$ and $\beta$, respectively, while $\gamma$ regulates how 
sharp the transition is from the lower to the higher ends.
The best fit parameters are as follows:
\begin{eqnarray}
\mathcal{M}_0  &=&  6.76 \times 10^{10} \nonumber \\
f_0  &=&   0.336 \nonumber \\
\alpha  &=&   0.684 \\
\beta  &=&   0.205 \nonumber \\
\gamma  &=&   3.40\nonumber  
\end{eqnarray}
The green shaded region indicates the scatter about the best fit line,
which is 0.151 {\bf dex} for haloes with mass in the range of  
$3\times 10^{9}\Msun < M_{200} <2\times 10^{10} \Msun$, 0.236 for
halo mass in 
$2\times 10^{10}\Msun < M_{200} < 7\times 10^{10} \Msun$,
0.125 for halo mass in
$7\times 10^{10}\Msun < M_{200} < 3\times 10^{11} \Msun$
and 0.0518 for halo mass in
$3\times 10^{11}\Msun < M_{200} < 3.5\times 10^{12} \Msun$.

As might be expected, haloes with the highest masses we study have
high baryon fractions with relatively  small scatter. As halo mass
decreases, the baryon fraction decreases and the scatter increases,
consistent with expectations from outflows driven by stellar
feedback {\bf since the energy-driven wind model determined that
mass loading factors show a power-law dependency on circular velocity
, with an exponent of $\approx -2$, \eg \citet{Christensen16}, 
which means the greater efficiency of small galaxies at 
driving outflows is simply a result of their shallower potential 
well and the increasing scatters come from the increasing scatters of
stellar mass halo mass relation in lower mass range.}
At the lowest halo masses we study, below $10^{10}\Msun$,
the scatter starts to decrease. By contrast the scatter in the stellar
mass fraction increases below this scale. Thus it seems unlikely that
stellar feedback is primarily responsible for the low baryon
fractions.  Rather, we suggest an increased importance of the UV
background, which heats gas to above the virial temperature, thus
preventing it from collapsing into the low mass haloes. 
{\bf Although the three most massive galaixes in NIHAO suite have fairly 
high stellar masses (see blue filled circles in Fig.~\ref{fig:budget}),
they don't have large deviations apart from the fitting baryon fraction, 
and in the comparason with FIRE (see Fig.~\ref{fig:fire_com}), these
three objects seem to hint the trend on massive galaxy end associated
with the data from \citet{Voort16}. Moreover, the fitting relation 
about the baryon fraction is not sensitive to these three most massive 
galaxies as well since they have equal weight with other more than 
80 galaxies to shape the fitting curve.}

{\bf Since the resolution is one key parameter in simulation, and one
can imagine that with increased resolution, higher densities can be 
achieved in the CGM, potential leading to more cooling and larger
cold/cool gas fraction,
the convergence of the baryonic fraction predicted by NIHAO suite
is worth to estimate. Fig.~\ref{fig:budget_res} shows cold and cool
gas (HI + HeI) fraction color coded by number of dark matter particles 
per halo. In the plot, the number of dark matter partilce per halo spans 
2 magnitudes and has no correlation with cold and cool gas fraction. 
Therefore, we can conclude the resolution of NIHAO suite is 
proper to study the fractional baryon content.}

@@

%% FIGURE 2
\begin{figure*}
\centerline{
  \psfig{figure=budgetpro.eps,width=1.0\textwidth}
}
\caption{Radial profile of the mass fraction of the gas in each phase
         to total baryonic mass in each radial bin 
         at $z=0$ for all galaxies in NIHAO sample.
         Each solid line is from one galaxy and colour coded with
         the halo mass.}
\label{fig:corona}
\end{figure*}

In Fig.~\ref{fig:corona}, we present the radial distribution of
gas in different phases at $z=0$, normalized to the total baryonic
mass profile, such that, in the region far away from central galaxy
where the stars are rare, for a given halo the four phases add up to
unity, {\bf each line is colour coded to the virial mass}.  
All simulations share a common attribute.  The cold gas (T$<
10^4$ K) is mostly located  near the center  ($R < 0.2 R_{200}$)
where most stars in galaxies form.  In contrast, the cool ($10^4$K
$<$ T $<$ $10^5$K) and  warm-hot ($10^5$K $<$ T $<$ $10^7$K) gas are
located at large distances with roughly constant fractions up to 2
times $R_{200}$.  The hot gas (T$>10^7$K) is a minority component
for all galaxies in the NIHAO sample, with the maximum hot gas
fraction at any radius being  less than 5\%.

Despite these similarities, we find a considerably higher proportion
of cool gas in lower mass galaxies (M$_{200} < 10^{11} \Msun$)
in the whole corona region.  For higher mass galaxies, warm-hot gas
dominates the corona  which signals {\bf stronger virial shock} and
higher efficiency  of feedback.
Even beyond the virial radius, the cool and warm-hot gas has similar
features as the gas within virial radius which reveals the gas
surrounding galaxies within large distance is the major reservoir of
baryons.

>>>>

\voffset=-0.4in

@@

\date{submitted to MNRAS}

\pagerange{\pageref{firstpage}--\pageref{lastpage}}\pubyear{2016}

@@

\begin{abstract}
  We use the NIHAO galaxy formation simulations to make predictions
  for the baryonic budget  in present day galaxies ranging from dwarf
  ($\Mhalo\sim10^{10} \Msun$) to Milky Way ($\Mhalo\sim10^{12} \Msun$)
  masses.  The sample is made of 88 independent high resolution
  cosmological zoom-in simulations.  NIHAO galaxies reproduce key
  properties of observed galaxies, such as the stellar mass vs halo
  mass and cold gas vs stellar mass relations. Thus they make
  plausible predictions for the baryon budget.  We present the mass
  fractions of stars, cold gas ($T<10^4$K), cool gas ($10^4 < T <
  10^5$K), warm-hot gas ($10^5 < T < 10^7$K), and hot gas (T$> 10^7$K)
  , inside the virial radius, $R_{200}$.  Compared to the predicted
  baryon mass, using the dark halo mass and the universal baryon
  fraction, $f_{\rm b}\equiv \Omega_{\rm b}/\Omega_{\rm m}=0.15$, we
  find that all of our haloes are missing baryons. The missing mass
  has been relocated past 2 virial radii, and {\bf cool gas dominates
    the corona at low mass (M$_{200} \lta 3 \times 10^{11} \Msun$)
    while the  warm-hot gas dominates dominates at high mass (M$_{200}
    \gta 3 \times 10^{11} \Msun$)}.  Haloes of mass $\Mhalo\sim
  10^{10}\Msun$ are missing $\sim 90\%$ of their baryons.  More
  massive haloes ($\Mhalo\sim 10^{12}\Msun$) retain a higher fraction
  of their baryons, with $\sim 30\%$ missing, consistent with recent
  observational estimates.  {\bf Moreover, these more massive haloes
    reproduce the observed  fraction of cold, warm-hot and hot gas.
    The fraction of cool gas we predict (0.11) is significantly lower
    than the observation from COS-HALOs (0.3-0.47), but agrees with
    the alternative analysis of \citet{Stern16}}.
\end{abstract}

@@

%% missing baryon problem
On cosmological scales, the ratio between the total baryonic and
gravitating mass is measured to be $f_{\rm b}\equiv \Omega_{\rm
  b}/\Omega_{\rm m}\simeq 0.15$ (The Planck Collaboration 2014).
However, the cold baryonic mass density implied by several galaxy
baryon estimates {\bf (mainly stars and cold gas)} is only 3-8\% of
the big bang nucleosynthesis expectation \citep{Persic92, Fukugita98,
  Bell03, McGaugh10}.  The majority of the cosmic baryons are thought
to be in the form of hot gas around or between galaxies
\citep{Cen09}. Until recently only a fraction of these baryons had
been detected \citep{Bregman07, Shull12}.  This discrepancy is
referred to as the ``missing baryon problem''.  Several theoretical
studies with cosmological simulations have constrained the phase of
the potential reservoirs of the missing baryons {\bf in the
  intergalactic medium (IGM), and find a large fraction of the baryons
  with low density and high temperature resides between galaxies}
\citep{Yoshida05, He05, Dave10, Zhu11, Haider16}.

The circum galactic medium (CGM) is {\bf another}  major potential
reservoir of the missing baryons. \hi{} and metal absorption lines are
expected  to signpost such diffuse baryonic content. \hi{} is mainly
from gas with temperature T $\sim 10^4$ K so that it is able to detect
cold gas in the CGM.  Meanwhile, theoretical work has predicted that a
substantial  portion of the CGM is in the warm or hot phase with
temperature T $> 10^{4.5}$ K.  Gas enters this phase through
photoionization, accretion shocks or shocks caused by galactic winds
\citep{Voort12}. Such dilute halo gas is at T$\sim 10^{4.5-7}$ K, so
the detection is dominated by metal lines, e.g. \ovi{}.  Recent
advances in the detection of gas in the CGM have come  from the COS
survey \citep{Tumlinson11, Tumlinson13, Thom12,  Werk12, Werk13}.  On
the scale of Milky Way mass haloes $\Mhalo \sim 10^{12}\Msun$ a
significant amount of warm ($10^4 < T < 10^7$K) gas has been detected
\citep{Werk14}, accounting for 33-88\% of the baryon budget. In the
future such observations will be extended to a wider range of halo
masses.  A number of large volume cosmological simulations
\citep{Ford13, Ford15, Suresh15b, Oppenheimer16} and zoom-in
cosmological simulations \citep{Stinson12, Hummels13, Shull14} have
given  predictions for the \hi{} and \ovi{} absorption
line. \citet{Gutcke16} compared the column density profile of \ovi{}
and \hi{} in the CGM of galaxies from the NIHAO \citep{Wang15}
cosmological hydrodynamical simulation suite with observations,
studied the covering fraction of dense \hi{}, looked at the shape of
the CGM and its chemical composition. {\bf The simulations
  reproduce  the observational covering fraction and column density
  profile of cool \hi{} well, and recover the observed trends of
  \ovi{} column density with luminosity and impact parameter. In
  common with other simulations, however, the column density of \ovi{}
  is lower and the extent of optically thick \hi{} is smaller than
  observed.}

The physical properties of the CGM has been shown to be able to
test feedback models \citep{Sharma12,Marasco13}.  \citet{Dave09}
predicted galactic halo baryon fractions of galaxies with halo
masses ranging from $10^{11} \Msun$ to $10^{13} \Msun$ using
cosmological hydrodynamical simulations with a well-constrained
model for galactic outflows.  They found that, without the outflow
model, the baryon fraction inside the virial radius is roughly the
cosmic baryonic fraction, but with the outflow model, the baryon
fraction is increasingly suppressed in lower mass haloes.  By
comparing results at $z=3$ and $z=0$, they showed that large
haloes remove their baryons at early times while small haloes lose
baryons more recently due to the wind material taking longer to
return to low-mass galaxies than high-mass galaxies.
{\bf \citet{Muratov15} showed similar results that the gas and
baryon fractions are lower at lower redshift, after powerful
outflows at intermediate redshift $z \approx 0.5-2$ remove a large
amount of gas from the halo. \citet{Voort16} found the baryon fraction
and gas fraction are reduced compared to the cosmic baryon
fraction, especially in low mass haloes.}
%  
\citet{Sokolowska16} studied the halo gas of three Milky way-sized
galaxies using cosmological zoom-in simulations. They found that
most of missing baryons actually resides in warm-hot and hot gas
which contribute to 80\% of the total gas reservoir.  The recovered
baryon fraction within 3 virial radii is 90\%.  The warm-hot medium
is sensitive to the feedback model so that a reliable spatial
mapping of the warm-hot medium will provide  a stringent test for
feedback models.

@@

@@

In this study we use simulations from the NIHAO (Numerical
Investigation of a Hundred Astrophysical Objects) project
\citep{Wang15}.   The initial conditions are created to keep the same
numerical resolution across the whole mass range with typically a
million dark matter particles inside the virial radius of the target
halo at  redshift $z=0$.  The halos to be re-simulated at higher
resolution with baryons have been extracted from 3 different pure
N-body simulations with a box size of 60, 20 and 15 $h^{-1}$ Mpc
respectively.  We adopted the  latest compilation of cosmological
parameters from the Planck  satellite \citep{Planck14}.  More
information on the collisionless parent simulations, {\bf the force
  softenings and particle masses for the highest refinement level for
  each simulation} and sample  selection can be found in
\citet{Dutton14} and \citet{Wang15}.

@@

The star formation and feedback modeling follows what was used in the
MaGICC simulations \citep{Stinson13}.   {\bf The gas is converted into
  stars according to the Kennicutt-Schmidt Law when it satisfies a
  temperature and density threshold. Stars feed both metals and energy
  back into the ISM gas surrounding the region where they formed. SN
  feedback is implemented using the blastwave formalism described in
  \citet{Stinson06}. Pre-SN feedback is an attempt to consider
  radiation energy from massive stars. Heating is introduced
  immediately after massive stars form based on how much star light is
  radiated.  Our simulations use thermal feedback to provide pressure
  support and  increase gas temperature above the star formation
  threshold, and thus to decrease star formation.}  There are two
small changes in NIHAO simulations compared to MaGICC:
The change in  number of neighbors
and the new combination of softening length and  particle mass
increases the threshold for star formation from  9.3 to 10.3
cm$^{-3}$, the increase of pre-SN feedback efficiency $\epsilon_{\rm
  ESF}$, from 0.1 to 0.13.  More details on the star formation and
feedback modeling can be found in \citet{Wang15}.

%% FIGURE 1
\begin{figure}
\centerline{
  \psfig{figure=barbudget_linearlog.eps,width=0.48\textwidth}
}
\caption{Fractional baryon content of our NIHAO simulations  as a
  function of halo mass. The green points show the ratio between the
  baryonic mass (stars + gas) inside the virial radius and the total
  baryonic mass associated with the dark matter halo. The blue points
  show the corresponding fraction for the stars. The solid green line
  and shaded region shows a double power-law fit, together with the
  1$\sigma$ scatter. For the stellar mass fraction we show several
  relations from halo abundance matching.    The linear (upper panel)
  and logarithmic (lower panel) scales emphasize the large amount of
  ``missing'' baryons, and the power-law nature of the relations,
  respectively.}
\label{fig:budget}
\end{figure}

%% FIGURE 2
\begin{figure*}
\centerline{
  \psfig{figure=m500c_frac.eps,width=0.85\textwidth}
}
\caption{{\bf Comparison between baryon (upper panels) and stellar
    fractions (lower panels) in the NIHAO simulations (blue circles)
    with simulations from \citet{Voort16} (left, red pentagons) and
    \citet{Christensen16} (right, purple pentagons).}}
\label{fig:fire_com}
\end{figure*}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% SECTION 3 BARYON BUDGET
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

The trends of each component fraction are similar, in that  the
fractions are relatively low in low mass haloes, and increase as the
halo mass increases.  The main difference between the different
components is the slope, with the baryonic mass fraction having a
shallower slope than the stellar mass fraction.  This is because in
low mass haloes ($\Mhalo\sim 10^{10}\Msun$) most of the baryons are in
the form of gas, while in the highest mass haloes we study
($\Mhalo\sim 10^{12}\Msun$) {\bf a substantial amount of gas
has been turned into stars}.

Since most of the haloes we study are above the mass where the cosmic
UV background prevents gas from cooling, the missing baryons have most
likely been ejected from the central galaxies in supernova/stellar
feedback driven winds.  Although the lower mass galaxies have
converted a smaller fraction of their available baryons into stars,
and hence there is proportionally less energy available to drive an
outflow, they have expelled a larger fraction of their baryons. {\bf
  This is consistent with expectations from energy driven gas
  outflows, where the lower star formation efficiency is more than
  compensated by the shallower potential wells of lower lower mass
  halos according the mass loading factor and circular velocity 
  relaion $\eta \propto V^{-2}$
   \citep[e.g.,][]{Dutton12, Christensen16}.}

The behavior of the baryonic mass fraction, $f_{\rm bar}$, as a 
function of the halo mass is captured using a double power law formula:
\begin{equation}
\frac{f}{f_0} = \left( 
                        \frac{M_{200}}{\mathcal{M}_0} 
                        \right)^\alpha 
                        \left\{ 0.5 \left[ 1+\left( 
                        \frac{M_{200}}{\mathcal{M}_0} 
                        \right)^\gamma \right] 
                        \right\}^{\frac{\beta-\alpha}{\gamma}}.
\end{equation}
In this formula, the lower and higher mass ends have logarithmic slope
$\alpha$ and $\beta$, respectively, while $\gamma$ regulates how 
sharp the transition is from the lower to the higher ends.
Giving all points equal weight, the best fit parameters are as follows:
\begin{eqnarray}
\mathcal{M}_0  &=&  6.76 \times 10^{10} \nonumber \\
f_0  &=&   0.336 \nonumber \\
\alpha  &=&   0.684 \\
\beta  &=&   0.205 \nonumber \\
\gamma  &=&   3.40\nonumber  
\end{eqnarray}

{\bf The three most massive galaxies in the NIHAO suite have fairly high
  stellar masses compared to abundance matching results (see blue
  filled circles in Fig.~\ref{fig:budget}), and are thus possibly
  overcooled.  However, they don't significantly bias the baryon
  fraction fitting formula since the high mass slope ($M_{200} >
  10^{11}\Msun$) is constrained by $\sim 40$ other haloes.}

The green shaded region indicates the scatter about the best fit line,
which is 0.151 {\bf dex} for haloes with mass in the range of  
$3\times 10^{9}\Msun < M_{200} <2\times 10^{10} \Msun$, 0.236 for
halo mass in 
$2\times 10^{10}\Msun < M_{200} < 7\times 10^{10} \Msun$,
0.125 for halo mass in
$7\times 10^{10}\Msun < M_{200} < 3\times 10^{11} \Msun$
and 0.052 for halo mass in
$3\times 10^{11}\Msun < M_{200} < 3.5\times 10^{12} \Msun$.

As might be expected, haloes with the highest masses  we study ($\sim
10^{12}\Msun$) have high baryon fractions ($\sim 0.7$) with relatively
small scatter (0.05 dex). As halo mass decreases, the baryon fraction
decreases and the scatter increases reaching a maximum of $\sim 0.24$
dex in haloes of mass $\sim 4\times10^{10}\Msun$.  However, at the
lowest halo masses we study, below $10^{10}\Msun$, the scatter starts
to decrease. By contrast the scatter in the stellar mass fraction
increases below this scale. Thus it seems unlikely that stellar
feedback is primarily responsible for the low baryon
fractions. Rather, we suggest an increased importance of the UV
background, which heats gas to above the virial temperature, thus
preventing it from collapsing into the low mass haloes. {\bf The
  baryon fractions are thus controlled primarily by the halo masses,
  and thus are independent of the large scatter in the star formation
  efficiency.}

%% FIGURE 3
\begin{figure*}
\centerline{
  \psfig{figure=budgetpro.eps,width=1.0\textwidth}
}
\caption{Radial profile of the mass fraction of the gas in each phase
         to total baryonic mass in each radial bin 
         at $z=0$ for all galaxies in NIHAO sample.
         Each solid line is from one galaxy and colour coded with
         the halo mass.}
\label{fig:corona}
\end{figure*}

\subsubsection{Comparison with other zoom-in simulations}
{\bf In Fig.~\ref{fig:fire_com} we compare the NIHAO results for the
  stellar and baryonic mass fractions with other recent
  state-of-the-art zoom-in simulations from \citet{Voort16} and
  \citet{Christensen16}.  Since these authors both use different halo
  mass definitions than we adopt here, we re-calculate the NIHAO
  results using a virial radius defined at $500\times$ critical
  density (left panels) and $100\times$ critical density (right
  panels).  The simulations analyzed in \citet{Voort16} are from the
  FIRE project \citep{Hopkins14}, which uses a different
  hydrodynamical code and different sub-grid model for star formation
  and feedback. The simulations analyzed in \citet{Christensen16} use
  a similar code as NIHAO, i.e.,  {\sc gasoline}, but with important
  differences. NIHAO uses an upgraded version that improves mixing
  \citep{Keller14}, and includes stronger feedback which was found to
  be necessary to delay star formation at early times
  \citep{Stinson13}. Despite these different codes employed, the
  baryon fractions in the three sets of simulations are in remarkably
  good agreement.

For the massive haloes with  M$_{500} > 10^{12} \Msun$, there are
three galaxies from NIHAO and four from FIRE.  There is a hint that
more massive haloes have lower baryon fractions.  Of course the caveat
here is that neither NIHAO or FIRE includes AGN feedback, which could
have a significant impact on the gaseous content of these haloes.

For the stellar fractions, \citet{Voort16} shows almost the same
result as our work. Even at the low mass end, their two lowest mass
galaxies may suggest the  large scatter as found in NIHAO.  However,
\citet{Christensen16} predicts one magnitude higher stellar fractions
than what we find for halo  masses below $10^{11.5}
\Msun$. This difference is likely due to the additional early stellar
feedback included in the NIHAO version of gasoline.

In summary, while the stellar mass fractions are dependent on the
sub-grid models, the baryon fractions (for haloes in the mass range
$10^{10}\lta M_{200} \lta 10^{12}\Msun$) appear insensitive to the
details of the simulation code. In particular all three codes predict a
greater fraction of missing baryons in lower mass haloes. This
suggests that the potential well of the halo regulates the baryon
fraction more than the strength of the feedback.  }

@@

In Fig.~\ref{fig:corona}, we present the radial distribution of
gas in different phases at $z=0$, normalized to the total baryonic
mass profile, such that, in the region far away from the central galaxy
where the stars are rare, for a given halo the four phases add up to
unity, {\bf each line is colour coded by the virial mass}.  
All simulations share a common attribute.  The cold gas (T$<10^4$K)
is mostly located  near the center  ($R<0.2R_{200}$)
where most stars in galaxies form.  In contrast, the cool ($10^4$K$<$T$<10^5$K)
and  warm-hot ($10^5$K$<$T$<10^7$K) gas are
located at large distances with roughly constant fractions up to 2
times $R_{200}$.  The hot gas (T$>10^7$K) is a minority component
for all galaxies in the NIHAO sample, with the maximum hot gas
fraction at any radius being  less than 5\%.

Despite these similarities, we find a considerably higher proportion
of cool gas in lower mass galaxies (M$_{200} < 10^{11} \Msun$) in the
whole corona region.  For higher mass galaxies, warm-hot gas dominates
the corona  which signals {\bf stronger virial shocks} and higher
efficiency  of feedback.  Even beyond the virial radius, the cool and
warm-hot gas has similar features as the gas within virial radius
which reveals the gas surrounding galaxies within large distances is
the major reservoir of baryons.
